---
title: "Final Project Part B"
format: docx
editor: visual
---
# Biostat213 Summer 2023 

First: Peijun

Last: Liu

## Read data

```{r}
Final<-read.csv("/Users/petra/Desktop/study/UCSF/BIOSTAT 213/ObesityDataSet.csv")

```

## Summary

[1pt] Print the structure of 'hf':

```{r}
str(Final)
```

## Identify up to 4 categorical and up to 4 continuous variables of your choice

```{r}
sapply(Final, class)

#4 categoricalvariables: 'Gender','family_history_with_overweight','SMOKE','NObeyesdad'
#4 continuous variables: 'Age','Height','Weight','FAF'
```

## For each categorical variable, print counts for each level
```{r}
for (i4 in c('Gender','family_history_with_overweight','SMOKE','NObeyesdad')){
  print(table(Final[[i4]]))
}
```

### For each categorical variable, make a barplot of counts
```{r}

barplot(table(Final$Gender))
barplot(table(Final$family_history_with_overweight))
barplot(table(Final$SMOKE))
barplot(table(Final$NObeyesdad))
```

### For each continuous variable, print mean, median, and standard deviation
```{r}
for (i5 in c('Age','Height','Weight','FAF')){
  cat(i5," : ","mean",mean(Final[[i5]])," ","median",median(Final[[i5]])," ","standard deviation",sd(Final[[i5]]),"\n")
}

```
## For each continuous variable, plot its distribution using a boxplot or a histogram (pick one type of plot and use it for all continuous variables)
```{r}
par(mfrow = c(1, 4))
hist(Final$Age, col = "#052049bb", border = "white", main = "")
hist(Final$Height, col = "#052049bb", border = "white", main = "")
hist(Final$Weight, col = "#052049bb", border = "white", main = "")
hist(Final$FAF, col = "#052049bb", border = "white", main = "")
```
